\documentclass{article}
\usepackage[T1]{fontenc}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
%
%----------------------------------------------------------------------------
%
\usepackage{listings}
\lstset{%
  basicstyle=\scriptsize\rmfamily\color{black},
%  commentstyle=\scriptsize\rmfamily\color{black},
%  commentstyle=\footnotesize\itshape,
  escapeinside={(*@}{@*)},
  numbers=left,
  xleftmargin=15pt,
  xrightmargin=5pt,
  numbersep=5pt,
  breaklines=true,
  moredelim=**[is][\ttfamily\bfseries\color{red}]{(*}{*)},
  tabsize=2,
  showstringspaces=false,
}
%
%----------------------------------------------------------------------------
%
\usepackage{syntax}
\usepackage[]{caption}
\usepackage{textcomp}
\usepackage{subcaption}
\usepackage{paralist}
\usepackage{xcolor}
\usepackage{colortbl}
\usepackage{graphicx}
\usepackage{enumerate}
\usepackage{amsfonts}
\usepackage{pifont}
\usepackage[sans]{dsfont}
\usepackage{mathtools}
\usepackage{multirow}
%\usepackage[keeplastbox]{flushend}
\usepackage{flushend}
\usepackage{hyperref}
\usepackage{realboxes}
\usepackage{booktabs}
%
%----------------------------------------------------------------------------
%
\usepackage{pbox}
%
%----------------------------------------------------------------------------
%
% Glossary
%
	\usepackage{glossaries}
	\input{glossaries}
%
%----------------------------------------------------------------------------
%
% TikZ packages and libaries
%
\usepackage{tikz}
\usepackage{tikz-timing}
\usepackage{etoolbox}
\usetikzlibrary{mindmap}
\usetikzlibrary{shapes}
\usetikzlibrary{arrows}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{decorations}
\usetikzlibrary{shapes.symbols}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{shapes.multipart}
\usetikzlibrary{positioning}
\usetikzlibrary{patterns}
\usetikzlibrary{calc}
\usetikzlibrary{scopes}         % cf. pgfmanual p.66
\usetikzlibrary{chains}         % cf. pgfmanual p.284
\usetikzlibrary{fit}
\usetikzlibrary{matrix}
\usetikzlibrary{decorations}
\usetikzlibrary{circuits.logic}
\usetikzlibrary{circuits.logic.IEC}
\usetikzlibrary{shapes.gates.logic.IEC}
\usetikzlibrary{circuits.logic.US}
\usetikzlibrary{shapes.gates.logic.US}
\usetikzlibrary{circuits.ee}
\usetikzlibrary{circuits.ee.IEC}
\usetikzlibrary{backgrounds}
\usetikzlibrary{automata}
\usetikzlibrary{intersections}
\usetikzlibrary{plotmarks}
\usepgflibrary{fpu}
\usetikzlibrary{decorations.pathreplacing}
%
%----------------------------------------------------------------------------
%
% Tables
%
\usepackage{tabularx}
\usepackage{makecell}
%
% Add vertical space to tabular
%
\renewcommand{\arraystretch}{1.5}
%
%----------------------------------------------------------------------------
%
% TikZ Trees
%
\usepackage{forest}
\usepackage{tikz-qtree}
%
%----------------------------------------------------------------------------
%
% Clever references
%
\usepackage{cleveref}
%
%
%----------------------------------------------------------------------------
%
%
% ToDo notes
%
\usepackage{todonotes} % to disable the todonotes uncomment line below
%\usepackege[disable]{todonotes}
\newcommand{\note}[1]{\todo[inline,linecolor=red,backgroundcolor=yellow!25,bordercolor=black]{AD: #1}}
%
%
%----------------------------------------------------------------------------
%
% Define custom sectioning - 4 level
%
\usepackage{titlesec}

\titleclass{\subsubsubsection}{straight}[\subsection]

\newcounter{subsubsubsection}[subsubsection]
\renewcommand\thesubsubsubsection{\thesubsubsection.\arabic{subsubsubsection}}

\titleformat{\subsubsubsection}
{\normalfont\normalsize\bfseries}{\thesubsubsubsection}{1em}{}
\titlespacing*{\subsubsubsection}
{0pt}{3.25ex plus 1ex minus .2ex}{1.5ex plus .2ex}

\makeatletter
\renewcommand\paragraph{\@startsection{paragraph}{5}{\z@}%
	{3.25ex \@plus1ex \@minus.2ex}%
	{-1em}%
	{\normalfont\normalsize\bfseries}}
\renewcommand\subparagraph{\@startsection{subparagraph}{6}{\parindent}%
	{3.25ex \@plus1ex \@minus .2ex}%
	{-1em}%
	{\normalfont\normalsize\bfseries}}
\def\toclevel@subsubsubsection{4}
\def\toclevel@paragraph{5}
\def\toclevel@paragraph{6}
\def\l@subsubsubsection{\@dottedtocline{4}{7em}{4em}}
\def\l@paragraph{\@dottedtocline{5}{10em}{5em}}
\def\l@subparagraph{\@dottedtocline{6}{14em}{6em}}
\makeatother

\setcounter{secnumdepth}{4}
\setcounter{tocdepth}{4}
%
%
%----------------------------------------------------------------------------
%

\title{Dynamic Partial Reconfiguration on an IOT device\\
\vspace{1em}
Android on Zynq featuring updatable FPGA-accellerated image processing \\ improved version }

\author{Andreas \textsc{Dejmek}}

\date{Summer-Term 2020}
\begin{document}
\maketitle
\begin{center}
	Supervised by:

	Nima \textsc{Taherinejad}
	
\end{center}
\begin{abstract}
	Hardware products are hard to update after they have been shipped.
	Reconfigurable devices such as FPGAs or CPLDs can be updated, but to
	update a whole system, the system needs to be shut down.
	%
	Often, only parts of a system need updating.
	This is possible with dynamic partial reconfiguration.
	The designer has to partition the given design and can then update
	partitions during runtime.
	%
	Applying dynamic partial reconfiguration to high level designs is not
	trivial.
	%
	We show how this can be done using the example of a Xilinx Zynq UltraScale+ MPSoC ZCU102 Evaluation Kit running the
	Android Operating System on it's integrated ARM cores and some image
	processing filters on the programmable logic.
	%
	We found that many customisation have to be made to the Linux kernel
	and the Android operating system.
	The choice of hardware restricted us to the use of outdated tools that
	made development difficult.
	%
	The methods can be applied to more state of the art chips to obtain
	powerful consumer multimedia devices with updatable hardware
	accelerators.
	\note{reword for new project}
\end{abstract}
\begin{center}
	Submitted in the "System on Chip Advanced Course" at TU Wien

%	\vspace{1em}

\end{center}
\pagebreak
\tableofcontents
\pagebreak
\section{Introduction}\label{sec:introduction}
\input{sections/introduction/introduction}
\section{Methodology}\label{sec:methodology}
\input{sections/methodology/methodology}
\section{Known Issues}\label{sec:knownissues}
\input{sections/knownissues/knownissues}
\section{Future Improvements}\label{sec:futureimprovements}
\input{sections/futureimprovements/futureimprovements}
\section{Conclusion}\label{sec:conclusion}
\input{sections/conclusion/conclusion}
\bibliographystyle{IEEEtran}
\bibliography{bib/soc}
\end{document}
