The Digilent ZedBoard is a developement Platform for the Xilinx Zynq \gls{soc}.
It features a dual-core ARM Cortex-A9 MPCore with a clock-frequency of up to
$866 Mhz$, external memory support, USB and Gigabit Ethernet interfaces as
\gls{ps} and \gls{pl} based on the Xilinx Artix-7 \gls{fpga} series.
The \gls{pl} can be used stand-alone, but the \gls{ps} is dependent on the
\gls{pl}.

For this project, the \gls{pl} needs to be configured with peripherals for the
processor that are needed by the Linux kernel as well as the hardware
accelerators.
The resulting system must then be partitioned for the dynamic partial
reconfiguration.
This is discussed in \Cref{ssec:zynqhardwaredesign}.

The \gls{ps} needs to be configured with all the software that Android needs to
boot, to interact with the hardware accelerators and to dynamically reconfigure
the \gls{pl}.
This is done in \Cref{ssec:zynqsoftwaredesign}.

The complete design is available as a git repository at~\cite{repo}.
File paths within this document may refer to the root directory of the git
repository by using \emph{<repo>}.
To interact with the ZedBoard, multiple interfaces are used:
\begin{itemize}
	\item A command line interface is available over an \gls{uart} interface
	\item Ethernet is used to access the internet
	\item Graphical output is available over a \gls{hdmi}
	\item Peripherals can be attached via \gls{otg}
\end{itemize}
To achieve the best android experience, a touchscreen is attached via \gls{hdmi}
(for graphics) and \gls{otg} (for the \gls{hid}).

To automate the extensive build process, two scripts are available in our git
repository.
\emph{<repo>/bootimage/generate\_without\_android.sh} compiles the bitstream,
\gls{fsbl}, u-boot, the linux kernel and the kernel modules.
Android is built seperately, since it requires a special build environment that
not all members of the team had access to.
To build android, the script
\emph{<repo>/bootimage/generate\_including\_android.sh} can be executed.

Both scripts rely on makefiles of the underlying components they are building.
This means that components that were not changed since the last build are not
going to be recompiled.
This saves build time during development.
\subsection{Zynq Hardware Design}\label{ssec:zynqhardwaredesign}
\input{sections/methodology/zynqhardwaredesign}
\subsubsection{Blake2B Module}\label{sssec:blake2bmodule}
\input{sections/methodology/blake2bmodule}
\subsubsection{Image Processing Module}\label{sssec:imageprocessingmodule}
\input{sections/methodology/imageprocessingmodule}
\subsubsection{Partial Reconfiguration Setup}\label{sssec:partialreconfigurationsetup}
\input{sections/methodology/partialreconfigurationsetup}
\subsection{Zynq Software Design}\label{ssec:zynqsoftwaredesign}
\input{sections/methodology/zynqsoftwaredesign}
\subsubsection{Linux on ZedBoard}\label{sssec:linuxonzedboard}
\input{sections/methodology/linuxzedboard}
\subsubsection{Android on ZedBoard}\label{sssec:androidonzedboard}
\input{sections/methodology/androidzedboard}
\subsubsection{Linux Kernel Modules}\label{sssec:linuxkernelmodules}
\input{sections/methodology/linuxkernelmodules}
\subsection{Image Processing App}\label{sssec:imageprocessingapp}
\input{sections/methodology/imageprocessingapp}
\subsection{Setup}\label{ssec:setup}
\input{sections/methodology/setup}
\subsubsection{Dynamic Partial Reconfiguration in Android}\label{sssec:dynamicpartialreconfiguration}
\input{sections/methodology/partialreconfiguration}
